Structured Versus Decorated Cospans

### 2020-11-11 cospans.tex
changed section title

\section{A symmetric monoidal double category of decorated cospans}\label{DecCospansDoubleCat}
In this section we build the symmetric monoidal double category $F \mathbb{C}$sp mentioned in the introduction. Then we obtain an underlying symmetric monoidal bicategory $F \mathbf{Csp}$ using a result of Shulman \cite{Shul} and finally decategorify this to obtain a symmetric monoidal category $F\mathsf{Csp}$ which is a generalization of Fong's original decorated cospan category \cite{Fong}.  The definition of a lax monoidal pseudofunctor is recalled in \cref{sec:2cats}, and the basics of double categories are recalled in \cref{sec:doublecats}.

>>>>

\section{Decorated cospans}\label{DecCospansDoubleCat}
In this section we build the symmetric monoidal double category $F \mathbb{C}$sp mentioned in the introduction. Then we obtain an underlying symmetric monoidal bicategory $F \mathbf{Csp}$ using a result of Shulman \cite{Shul} and finally decategorify this to obtain a symmetric monoidal category $F\mathsf{Csp}$ which is a generalization of Fong's original decorated cospan category \cite{Fong}.  The definition of a lax monoidal pseudofunctor is recalled in \cref{sec:2cats}, and the basics of double categories are recalled in \cref{sec:doublecats}.
